Human Factors Influencing Visual Statistical Inference

### 2013-06-12 sociology_paper.tex
reference updated

\subsection{Signal in the data}

@@

\subsubsection{Design for Location effect} The experiment was set up based on the gene expression data \citep{atwood:2013} with two groups. The groups are defined based on the Genotype and Empty Vector (EV). For each of the of the Genotype, gene expression data were collected in presence or absence of iron sufficiency. Two hypothesis were of primary interest. The Genotype main effect and the Genotype and iron sufficiency interaction effect.

@@

\subsection{Data collection methods}  Human observers were recruited to evaluate the experimental lineups through Amazon Mechanical Turk \cite{turk} or MTurk Web site.  It is an online work place where people from around the world can perform some tasks and get paid. Usually tasks are very simple and no specialized training is required. Being a human is the main requirement. Tasks are designed for anyone to do but some tasks may require that workers satisfy some skill level depending on the recruiters need. The tasks are designed such that it does not take much time to complete. Humans are still better than computers in performing these types of tasks. The the amount of money paid for each task is very small as well.

@@

\section{Some figures and tables (May go to Appendix)}

\subsection{How people pick the data plot} In the experiment setup we have a question for the turk observers to choose the reason for their selection of a particular data plot. It is shown by \cite{majumder:2013} that these choice reasons reveal the way people picks the data plot in the lineup. To investigate this further we added free text input option for their choice reason instead of some fixed reasons to select from. In this experiment people could write whatever they think their reasons for choice are. Figure \ref{fig:wordle} shows the words used to explain their reasons for choice. The most common words used to explain their choice are points and green which indicates two important feature of a plot. One is the indicator of plot aesthetics and the other is the color. Spread, steepest, line and apart are some other important words used frequently. Spread and apart are indicative of variability in the data. Steepest and line indicates some sort of systematic pattern in the data.

>>>>

\subsection{Signal in the Data}

@@

\subsubsection{Design for Location Effect} The experiment was set up based on the gene expression data \citep{atwood:2013} with two groups. The groups are defined based on the Genotype and Empty Vector (EV). For each of the of the Genotype, gene expression data were collected in presence or absence of iron sufficiency. Two hypothesis were of primary interest. The Genotype main effect and the Genotype and iron sufficiency interaction effect.

@@

\subsection{Data Collection Methods}  Human observers were recruited to evaluate the experimental lineups through Amazon Mechanical Turk \cite{turk} or MTurk Web site.  It is an online work place where people from around the world can perform some tasks and get paid. Usually tasks are very simple and no specialized training is required. Being a human is the main requirement. Tasks are designed for anyone to do but some tasks may require that workers satisfy some skill level depending on the recruiters need. The tasks are designed such that it does not take much time to complete. Humans are still better than computers in performing these types of tasks. The the amount of money paid for each task is very small as well.

@@

\section{Some Figures and Tables (May go to Appendix)}

\subsection{How People Pick the Data Plot} In the experiment setup we have a question for the turk observers to choose the reason for their selection of a particular data plot. It is shown by \cite{majumder:2013} that these choice reasons reveal the way people picks the data plot in the lineup. To investigate this further we added free text input option for their choice reason instead of some fixed reasons to select from. In this experiment people could write whatever they think their reasons for choice are. Figure \ref{fig:wordle} shows the words used to explain their reasons for choice. The most common words used to explain their choice are points and green which indicates two important feature of a plot. One is the indicator of plot aesthetics and the other is the color. Spread, steepest, line and apart are some other important words used frequently. Spread and apart are indicative of variability in the data. Steepest and line indicates some sort of systematic pattern in the data.
